---
title: "owner-analysis"
format: html
author: harrison
---

## Exercise: explore, clean, and wrangle data

```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(here)
```

read in lobster abundance data 

```{r}
lobster_abundance <- read_csv(here("data/Lobster_Abundance_All_Years_20220829.csv"))

head(lobster_abundance)
```
convert -99999.0 to nas

```{r}
lobster_abundance %>% 
  mutate(SIZE_MM = na_if(SIZE_MM, -99999))

```
Create and store a subset that does NOT include observations from Naples Reef (NAPL). Check your output data frame to ensure that NAPL is NOT in the data frame.

```{r}
lobster_abundance %>% 
  filter(SITE != "NAPL")
```

Create and store a subset with lobsters at Arroyo Quemado (AQUE) AND with a carapace length greater than 70 mm. Check your output.

```{r}
aque_long <- lobster_abundance %>% 
  filter(SITE == "AQUE") %>% 
  filter(SIZE_MM > 70)

head(aque_long)
```

Find the maximum carapace length using max() and group by SITE and MONTH. Think about how you want to treat the NA values in SIZE_MM (Hint: check the arguments in max()). Check your output.

```{r}
max_carapace <- lobster_abundance %>% 
  group_by(SITE, MONTH) %>% 
  summarize(max_length = max(SIZE_MM))

max_carapace
```




